---
title: "Lvl3 Data"
author: "A Clarke"
date: "16/09/2021"
output: html_document
---

```{r setup, include=FALSE}
library(tidyverse)
library(ggthemes)
library(brms)
library(tidybayes)
library(corrr)
library(patchwork)

options(digits = 2, mc.cores = 10)

knitr::opts_chunk$set(echo = TRUE)
theme_set(theme_bw())

source("plot_ddm_model.R")
```

# Data check and merge

## Import Data

```{r}
d <- read_csv("../data_collected_by_level_3/Rt_accuracy_extracted.txt") %>%
  select(-age, -sex, -n) %>%
  select(obs = "observer", type = "targetType", targ = "targetPres", nD = "numDist", rt, accuracy) %>%
  mutate(targ = as_factor(targ),
         targ = fct_recode(targ, absent = "0", present = "1"))
```

## Check Summary Statistics


```{r}
d %>% group_by(obs,  targ) %>%
  summarise(accuracy = mean(accuracy)) %>%
  filter(accuracy < 0.75) -> to_remove

to_remove
```

Looks like we should remove these two participants

```{r}
d <- filter(d, !(obs %in% unique(to_remove$obs)))
```

Let's look at the RTs...

```{r}
min_rt = 0.200
max_rt = 10.00

ggplot(d, aes(x = rt)) + geom_histogram(bins = 100) +
  geom_vline(xintercept = c(min_rt, max_rt), linetype = 2) +
  scale_x_log10() + 
  coord_cartesian(xlim = c(0.1, 10)) + 
  ggtitle("all RTs")

```



How doe these numbers look when compared to the histogram of all RTs.

```{r}

```

```{r}
d %>% 
  summarise(percent_below = 100*mean(rt<min_rt),
            percent_above = 100*mean(rt>max_rt),
            percent_removed = percent_below + percent_above) %>%
  knitr::kable()

d <- filter(d, rt>min_rt, rt<max_rt)
```


## Output for Modelling

We have already removed 
- the participant who was very inaccurate
- RTs < 0.250 seconds (0.2% of data)
- RTs > 250.0 seconds (0.06% of data)

Before we run our model, we have to recover the present/absent responses made for each trial (rather than accuracy)

```{r}
d$response <- NA
d$response[which(d$targ=="present" & d$accuracy==1)] = 1
d$response[which(d$targ=="present" & d$accuracy==0)] = 0
d$response[which(d$targ=="absent" & d$accuracy==1)] = 0
d$response[which(d$targ=="absent" & d$accuracy==0)] = 1
```

Finally, save the data before modelling.

```{r}
write_csv(d, "../cluster_level3/data_for_model.csv")
```


# Summary Stats

## Accuracy

```{r}
d %>% group_by(obs, type, targ, nD) %>% 
  summarise(accuracy = mean(accuracy)) %>%
  ggplot(aes(x = as.factor(nD), y = accuracy, fill = type)) + 
  geom_boxplot(alpha = 0.5) + 
  facet_wrap(~targ) +
  scale_fill_manual(values = c("#228833", "#EE6677")) +
  scale_x_discrete("number of distracters") +
  theme(legend.position = "bottom") -> plt_acc


d %>% group_by(obs, type, targ, nD) %>% 
  summarise(accuracy = mean(accuracy)) %>%
  filter(targ == "present", nD == 15) %>% 
  pivot_wider(values_from = "accuracy", names_from = "type") -> d2

ggplot(d2, aes(x = greenVertical, y = redHorizontal)) + 
  geom_jitter(alpha = 0.5, width = 0.005, height = 0.005) +
  geom_abline(linetype = 2) +
  coord_fixed(xlim = c(0.7, 1), ylim = c(0.7, 1)) +
  scale_x_continuous("green vertical") +
  scale_y_continuous("red  vertical") -> plt_acc2

plt_acc + plt_acc2 + plot_layout(widths = c(2, 1))

cor.test(d2$greenVertical, d2$redHorizontal)

#bayes_R2(brm(greenVertical ~ redHorizontal, data = d2))

```

## Reaction Time

```{r}
d %>% filter(accuracy == 1) %>%
  group_by(obs, type, targ, nD) %>%
  summarise(median_rt = median(rt)) -> drt


drt %>%
  ggplot(aes(x = nD, y = median_rt, colour = type)) + 
  geom_jitter(alpha = 0.5, width = 0.5, height = 0) + 
  facet_wrap(~targ) + 
  geom_smooth(method = "lm", se = FALSE, formula = y~x) + 
  scale_colour_manual(values = c("#228833", "#EE6677")) +
  scale_x_continuous("number of distracters") + 
  scale_y_continuous("median reaction time (seconds)") +
  theme(legend.position = "bottom") -> plt_rt


drt %>% group_by(obs, type) %>%
  summarise(mean_med_rt = mean(median_rt)) %>%
  pivot_wider(values_from = "mean_med_rt", names_from = "type") %>%
  ggplot(aes(x = greenVertical, y = redHorizontal)) + 
  geom_jitter(alpha = 0.5, width = 0.005, height = 0.005) +
  geom_abline(linetype = 2) +
  coord_fixed(xlim = c(0.5, 1.4), ylim = c(0.5, 1.4)) +
  scale_x_continuous("green vertical") +
  scale_y_continuous("red  vertical") -> plt_rt2

(plt_acc + plt_acc2) / (plt_rt + plt_rt2) + plot_layout(widths = c(2, 1), guides = "collect") & theme(legend.position = "none")
ggsave("../manuscript/figs/exp_lvl_3_emp.pdf", height = 6, width = 9)


```


# Model 1 (full)


```{r}
m <- readRDS("models/level3_full.model")
```

## Posterior Predections

```{r}
d %>%
  mutate(obs = as.factor(obs),
         nD = nD/max(nD)) -> d
# 
# pred_wiener <- d %>% add_predicted_draws(m,negative_rt = TRUE, n = 100) %>%
#   ungroup() %>%
#   select(-.chain, -.draw, -.iteration, -.row) %>%
#   mutate(rt = if_else(response == 1, rt, -rt)) %>%
#   pivot_longer(c(rt, .prediction), names_to = "emp_pre", values_to = "rt") %>%
#   select(-response, -accuracy) %>%
#   mutate(emp_pre = fct_recode(emp_pre, empirical = "rt", prediction = ".prediction"),
#                               response = if_else(rt < 0, "absent", "present"),
#                               response = as_factor(response),
#                               accuracy = response == targ,
#                               rt = abs(rt))
# write_csv(pred_wiener, "predictions_full.csv")

pred_wiener <- read_csv("predictions_full.csv")

ggplot(pred_wiener, aes(x = rt, fill = emp_pre)) + 
   geom_density(alpha = 0.25) + 
   facet_grid(nD~targ) +
   coord_cartesian(xlim = c(0, 2))

pred_wiener %>% group_by(obs, targ, type, nD, emp_pre) %>%
  summarise(median_rt = median(rt), .groups = "drop") %>%
  pivot_wider(names_from = "emp_pre", values_from = "median_rt") %>%
  ggplot(aes(x = prediction, y = empirical, colour = type)) + 
  geom_abline(linetype = 2) +
  geom_point(alpha = 0.5) + 
  coord_fixed() + 
  scale_colour_manual(values = c("#228833", "#EE6677")) +
  facet_wrap(~targ) +
  theme(legend.position = "none") -> plt_rt


pred_wiener %>% group_by(obs, targ, type, nD, emp_pre) %>%
  summarise(accuracy = mean(accuracy), .groups = "drop") %>%
  pivot_wider(names_from = "emp_pre", values_from = "accuracy") %>%
  ggplot(aes(x = prediction, y = empirical, colour = type)) + 
    geom_abline(linetype = 2) +
   scale_colour_manual(values = c("#228833", "#EE6677")) +
  facet_wrap(~targ) +
  coord_fixed(xlim = c(0.75, 1), ylim = c(0.75, 1)) + 
  geom_jitter(alpha = 0.25, height = 0.01)  +
  theme(legend.position = "none") -> plt_acc

plt_acc / plt_rt

ggsave("../manuscript/figs/exp_lvl_3_pred.pdf", height = 6, width = 5)
```


```{r}
m %>% gather_draws(`cor.*`, regex = TRUE) %>%
  rename(var = ".variable") %>%
  mutate(var = str_remove(var, "cor_observer__")) -> cor_post 

cor_post %>% group_by(var) %>%
    summarise(p_not_zero = max(mean(.value > 0), mean(.value < 0))) %>%
    mutate(p_not_zero = cut(p_not_zero, c(0.5, 0.8, 0.9, 0.95, 0.99, 1))) %>%
    full_join(cor_post, by = "var") %>%
  select(-.chain, -.iteration , -.draw) -> cp
```

## Plot Parameters

```{r}
plt_rate_fx <- plot_model_params(m, "drift rate")
plt_rate_rn <- plt_cors(cp, "drift rate") 

plt_bs_fx <- plot_model_params(m, "bs")
plt_bs_rn <- plt_cors(cp, "bs") 

plt_bias_fx <- plot_model_params(m, "bias")
plt_bias_rn <- plt_cors(cp, "bias") 
```

```{r, fig.width=10}
(plt_rate_fx + plt_bs_fx + plt_bias_fx) / (plt_rate_rn + theme(legend.position = "none") + plt_bs_rn + plt_bias_rn)  + plot_layout(guides = "collect") & theme(legend.position = "bottom")
ggsave("model_output.png", width = 10, height = 5)
```


# Model 2 (reduced)


```{r}
m <- readRDS("models/level3_redu.model")
```




## Posterior Predections

```{r}
# d %>%
#   mutate(obs = as.factor(obs),
#          nD = nD/max(nD)) -> d

# pred_wiener <- d %>% add_predicted_draws(m,negative_rt = TRUE, n = 100) %>%
#   ungroup() %>%
#   select(-.chain, -.draw, -.iteration, -.row) %>%
#   mutate(rt = if_else(response == 1, rt, -rt)) %>%
#   pivot_longer(c(rt, .prediction), names_to = "emp_pre", values_to = "rt") %>%
#   select(-response, -accuracy) %>%
#   mutate(emp_pre = fct_recode(emp_pre, empirical = "rt", prediction = ".prediction"),
#                               response = if_else(rt < 0, "absent", "present"),
#                               response = as_factor(response),
#                               accuracy = response == targ,
#                               rt = abs(rt))
# write_csv(pred_wiener, "predictions_redu.csv")

pred_wiener <- read_csv("predictions_redu.csv")

ggplot(pred_wiener, aes(x = rt, fill = emp_pre)) + 
   geom_density(alpha = 0.25) + 
   facet_grid(nD~targ) +
   coord_cartesian(xlim = c(0, 2))

pred_wiener %>% group_by(obs, targ, type, nD, emp_pre) %>%
  summarise(median_rt = median(rt), .groups = "drop") %>%
  pivot_wider(names_from = "emp_pre", values_from = "median_rt") %>%
  ggplot(aes(x = prediction, y = empirical, colour = type)) + 
  geom_abline(linetype = 2) +
  geom_point(alpha = 0.5) + 
  coord_fixed() + 
  scale_colour_manual(values = c("#228833", "#EE6677")) +
  facet_wrap(~targ) +
  theme(legend.position = "none") -> plt_rt


pred_wiener %>% group_by(obs, targ, type, nD, emp_pre) %>%
  summarise(accuracy = mean(accuracy), .groups = "drop") %>%
  pivot_wider(names_from = "emp_pre", values_from = "accuracy") %>%
  ggplot(aes(x = prediction, y = empirical, colour = type)) + 
    geom_abline(linetype = 2) +
   scale_colour_manual(values = c("#228833", "#EE6677")) +
  facet_wrap(~targ) +
  coord_fixed(xlim = c(0.75, 1), ylim = c(0.75, 1)) + 
  geom_jitter(alpha = 0.25, height = 0.01)  +
  theme(legend.position = "none") -> plt_acc

plt_acc / plt_rt

ggsave("../manuscript/figs/exp_lvl_3_pred.pdf", height = 6, width = 5)
```


```{r}
m %>% gather_draws(`cor.*`, regex = TRUE) %>%
  rename(var = ".variable") %>%
  mutate(var = str_remove(var, "cor_observer__")) -> cor_post 

cor_post %>% group_by(var) %>%
    summarise(p_not_zero = max(mean(.value > 0), mean(.value < 0))) %>%
    mutate(p_not_zero = cut(p_not_zero, c(0.5, 0.8, 0.9, 0.95, 0.99, 1))) %>%
    full_join(cor_post, by = "var") %>%
  select(-.chain, -.iteration , -.draw) -> cp
```

## Plot Parameters

```{r}
plt_rate_fx <- plot_model_params(m, "drift rate")
plt_rate_rn <- plt_cors(cp, "drift rate") 

plt_bs_fx <- plot_model_params(m, "bs")
plt_bs_rn <- plt_cors(cp, "bs") 

plt_bias_fx <- plot_model_params(m, "bias")
plt_bias_rn <- plt_cors(cp, "bias") 
```

```{r, fig.width=10}
(plt_rate_fx + plt_bs_fx + plt_bias_fx) / (plt_rate_rn + theme(legend.position = "none") + plt_bs_rn + plt_bias_rn)  + plot_layout(guides = "collect") & theme(legend.position = "bottom")
ggsave("model_output.png", width = 10, height = 5)
```
